A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-28 06_bat_data.Rmd
some minor section issues

![](figures/fig_bat_filter_cov.png)
## Filter by speed

@@

```{r}
# plot the raw, filtered, and smoothed data
fig_bat_smooth <- 
  ggplot()+
  geom_point(data = data[!data_split, 
                         on = c("TAG", "X", "Y", "TIME")],
             aes(X, Y),
             col = "grey",
             shape = 4)+
  geom_point(data = data_split,
             aes(X, Y),
             col = pal[3],
             alpha = 0.5,
             shape = 1,
             show.legend = FALSE)+
  geom_path(data = data_smooth,
            aes(X, Y,
                col = as.numeric(TAG)),
            lwd = 0.3,
            show.legend = FALSE)+
  scale_fill_distiller(palette = "Greens",
                       direction = 1)+
  scale_colour_distiller(palette = "Purples",
                         direction = 1,
                         values = c(-0.2, 1))+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 2039,
           xlim = range(data_smooth$X),
           ylim = range(data_smooth$Y))
```

@@

>>>>

![](figures/fig_bat_filter_cov.png)

## Filter by speed

@@

```{r}
# plot the raw, filtered, and smoothed data
fig_bat_smooth <- 
  ggplot()+
  geom_point(data = data_split,
             aes(X, Y),
             col = pal[3],
             alpha = 0.2,
             shape = 16,
             show.legend = FALSE)+
  geom_path(data = data_smooth,
            aes(X, Y,
                col = as.numeric(TAG)),
            lwd = 0.3,
            show.legend = FALSE)+
  scale_fill_distiller(palette = "Greens",
                       direction = 1)+
  scale_colour_distiller(palette = "Purples",
                         direction = 1,
                         values = c(-0.2, 1))+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 2039,
           xlim = range(data_smooth$X),
           ylim = range(data_smooth$Y))
```

Save the smoothed data plot.

@@

## Processed bat patches

![](figures/fig_bat_patches.png)
